Visual Diagnostics for Constrained Optimisation with Application to Guided Tours

### 2022-01-13 zhang-cook-laa-langrene-menendez.Rmd
move paper to the top level directory
fix PCA plot colour and caption

```{r external, include = FALSE, cache = FALSE}
knitr::read_chunk(
  here::here("paper", "script.R")
)
```

@@

```{r toy-pca, out.width = "70%", fig.cap = "Search paths of CRS (green) and PD (brown) in the PCA-reduced basis space for 1D projection problem on the five-variable dataset, \\code{boa5} using holes index. The basis space, a 5D unit sphere, is projected onto a 2D circle by PCA. The black star represents the theoretical best basis the optimisers are aiming to find. All the bases in PD have been flipped for easier comparison of the final bases, and a grey dashed line has been annotated to indicate the symmetry of the two start bases."}
```

@@

```{r toy-pca-animated, fig.cap = "Six frames selected from the animated version of the previous plot. With animation, the progression of the search paths from start to finish is better identified. CRS (green) finishes the optimisation quicker than PD (brown) since there is no further movement for CRS in the sixth frame. The full video of the animation can be found in the html version of the paper.", eval=knitr::is_latex_output()}
```

```{r toy-pca-animated-interactive, out.extra="class = 'gif'", fig.cap = "Animated version of Figure 4. With animation, the progression of the search paths from start to finish can better identified and CRS (green) finishes the optimisation quicker than PD (brown).", eval=knitr::is_html_output()}
```

>>>>

```{r external, include = FALSE, cache = FALSE}
knitr::read_chunk(
  here::here("script.R")
)
```

@@

```{r toy-pca, out.width = "70%", fig.cap = "Search paths of CRS (brown) and PD (green) in the PCA-reduced basis space for 1D projection problem on the five-variable dataset, \\code{boa5} using holes index. The basis space, a 5D unit sphere, is projected onto a 2D circle by PCA. The black star represents the theoretical best basis the optimisers are aiming to find. All the bases in PD have been flipped for easier comparison of the final bases, and a grey dashed line has been annotated to indicate the symmetry of the two start bases."}
```

@@

```{r toy-pca-animated, fig.cap = "Six frames selected from the animated version of the previous plot. With animation, the progression of the search paths from start to finish is better identified. CRS (brown) finishes the optimisation quicker than PD (green) since there is no further movement for CRS in the sixth frame. The full video of the animation can be found in the html version of the paper.", eval=knitr::is_latex_output()}
```

```{r toy-pca-animated-interactive, out.extra="class = 'gif'", fig.cap = "Animated version of Figure 4. With animation, the progression of the search paths from start to finish can better identified and CRS (brown) finishes the optimisation quicker than PD (green).", eval=knitr::is_html_output()}
```

### 2022-01-13 zhang-cook-laa-langrene-menendez.tex
fix PCA plot colour and caption

\caption[Search paths of CRS (green) and PD (brown) in the PCA-reduced basis space for 1D projection problem on the five-variable dataset, \code{boa5} using holes index]{Search paths of CRS (green) and PD (brown) in the PCA-reduced basis space for 1D projection problem on the five-variable dataset, \code{boa5} using holes index. The basis space, a 5D unit sphere, is projected onto a 2D circle by PCA. The black star represents the theoretical best basis the optimisers are aiming to find. All the bases in PD have been flipped for easier comparison of the final bases, and a grey dashed line has been annotated to indicate the symmetry of the two start bases.}\label{fig:toy-pca}
\end{figure}
\end{Schunk}

@@

\caption[Six frames selected from the animated version of the previous plot]{Six frames selected from the animated version of the previous plot. With animation, the progression of the search paths from start to finish is better identified. CRS (green) finishes the optimisation quicker than PD (brown) since there is no further movement for CRS in the sixth frame. The full video of the animation can be found in the html version of the paper.}\label{fig:toy-pca-animated}
\end{figure}
\end{Schunk}

>>>>

\caption[Search paths of CRS (brown) and PD (green) in the PCA-reduced basis space for 1D projection problem on the five-variable dataset, \code{boa5} using holes index]{Search paths of CRS (brown) and PD (green) in the PCA-reduced basis space for 1D projection problem on the five-variable dataset, \code{boa5} using holes index. The basis space, a 5D unit sphere, is projected onto a 2D circle by PCA. The black star represents the theoretical best basis the optimisers are aiming to find. All the bases in PD have been flipped for easier comparison of the final bases, and a grey dashed line has been annotated to indicate the symmetry of the two start bases.}\label{fig:toy-pca}
\end{figure}
\end{Schunk}

@@

\caption[Six frames selected from the animated version of the previous plot]{Six frames selected from the animated version of the previous plot. With animation, the progression of the search paths from start to finish is better identified. CRS (brown) finishes the optimisation quicker than PD (green) since there is no further movement for CRS in the sixth frame. The full video of the animation can be found in the html version of the paper.}\label{fig:toy-pca-animated}
\end{figure}
\end{Schunk}
